Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-20 outputs/paper/paper.Rmd
reference

# References
-- Smith, Tom W., Davern, Michael, Freese, Jeremy, and Morgan, Stephen L., General Social Surveys, 1972-2018 [machine-readable data file] /Principal Investigator, Smith, Tom W.; Co-Principal Investigators, Michael Davern, Jeremy Freese and Stephen L. Morgan; Sponsored by National Science Foundation. --NORC ed.-- Chicago: NORC, 2019.

-- U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.

U.S. Census Bureau quickfacts: United States. (n.d.), from https://www.census.gov/quickfacts/fact/table/US/PST045221

>>>>

# References
Smith, Tom W., Davern, Michael, Freese, Jeremy, and Morgan, Stephen L., General Social Surveys, 1972-2018 [machine-readable data file] /Principal Investigator, Smith, Tom W.; Co-Principal Investigators, Michael Davern, Jeremy Freese and Stephen L. Morgan; Sponsored by National Science Foundation. --NORC ed.-- Chicago: NORC, 2019.

U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.
